*flippant* --- An R package for the automated analysis of dithionite scramblase

### 2016-06-09 inst/manuscript/manuscript.rmd
Add a remark regarding "Force_through_origin" (is laready in the package doc);
Typo;

allows for the complete generation of the PPR plot in publication quality from
the user assembled spreadsheet of input data (`x`), including automatically
added graphical representations the PPR value equal to the fit constant
$\alpha$ ($P_{\geq 1} = 1 - e^{-1}$), which implies all liposomes on average
carrying one scramblase and 63% have one or more 
[i.e. are active; @goren_constitutive_2014]. The behavior of the function may be
adjusted to use scramblase--mediated fluorescence reduction normalized to either
the maximum measurement in the series (`scale_to = "data"`) or the plateau of an
exponential fit to it (`scale_to = "model"`; for reasoning see above) and whether
or not to require the exponential curve fitted to the data to go through the
origin. `ppr_scale_factor` allows for the modification of scaling to account for
a pool of vesicles that is scramblase--inaccessible (see above). The
`split_by_experiment` argument is used to indicate whether independent
experiments are integrated into a single analysis (`split_by_experiment = FALSE`)
or treated separately (`split_by_experiment = TRUE`; see below for example usage).

@@

```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
x <- flippant:::read_scramblase_input_file(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- add_panel(
  figure = figure1,
  top_panel = 1,
  bottom_panel = 3,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
figure1 <- add_panel(
  figure = figure1,
  top_panel = 4,
  bottom_panel = 5,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- add_panel(
  figure = figure1,
  top_panel = 6,
  bottom_panel = 7,
  left_panel = 1,
  right_panel = 2,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

>>>>

allows for the complete generation of the PPR plot in publication quality from
the user assembled spreadsheet of input data (`x`), including automatically
added graphical representations the PPR value equal to the fit constant
$\alpha$ ($P_{\geq 1} = 1 - e^{-1}$), which implies all liposomes on average
carrying one scramblase and 63% have one or more 
[i.e. are active; @goren_constitutive_2014]. The behavior of the function may be
adjusted to use scramblase--mediated fluorescence reduction normalized to either
the maximum measurement in the series (`scale_to = "data"`) or the plateau of an
exponential fit to it (`scale_to = "model"`; for reasoning see above) and whether
or not to require the exponential curve fitted to the data to go through the
origin. `ppr_scale_factor` allows for the modification of scaling to account for
a pool of vesicles that is scramblase--inaccessible (see above). The
`split_by_experiment` argument is used to indicate whether independent
experiments are integrated into a single analysis
(`split_by_experiment = FALSE`) or treated separately
(`split_by_experiment = TRUE`; see below for example usage). The
`force_through_origin` parameter may be used to employ a fit with more degrees
of freedom. While the non--default `force_through_origin = FALSE` allows for a
better fit to some experimental data, its mechanistic implications are unclear.

@@

```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
x <- flippant:::read_scramblase_input_file(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- add_panel(
  figure = figure1,
  top_panel = 1,
  bottom_panel = 3,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
figure1 <- add_panel(
  figure = figure1,
  top_panel = 4,
  bottom_panel = 5,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- add_panel(
  figure = figure1,
  top_panel = 6,
  bottom_panel = 7,
  left_panel = 1,
  right_panel = 2,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```
